---
title: "Infering species distribution from aggregated spatial data"
subtitle : "Going from coarse landings data to fine scale species distribution"
author : "Baptiste Alglave, Marie-Pierre Etienne, Kasper Kristensen, Youen Vermard,  Mathieu Woillez, Etienne Rivot"

fontsize: 10pt
bibliography : ["ref.bib"]
csl : ices-journal-of-marine-science.csl

output:
  beamer_presentation:
    theme: "Darmstadt"
    colortheme: "default"
    slide_level: 3
    # template: mytemplate.tex
    includes:
      in_header: header-simple.tex
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(rnaturalearth)
library(stringr)
library(sf)
library(raster)
library(maps)
library(mapdata)
library(ggplot2)
library(ggspatial)
library(cowplot)
library(latex2exp)
library(ggpubr)

col_scale <- function(palette = "Spectral", name = "", limits = NULL) {
  scale_colour_distiller(palette = palette,   # spectral colour scale
                         guide = "colourbar", # continuous colour bar
                         name = name,
                         limits = limits)
}

run_codes <- F

grid_projection <- "+proj=longlat +datum=WGS84"

mapBase <- map("worldHires", fill = T, plot = F)
mapBase <- st_as_sf(mapBase) %>% filter(ID %in% c("France","Spain"))

```


# Context

### Spatial data in ecology

<!-- Standardized and high quality data, but low amount of samples -->
<!-- more data, but no standardize sampling plan (e.g. problem related to preferential sampling) -->
<!-- legal and massive data, but low quality, declared at the level of some administrative unit -->

\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.3\textwidth}
\center {\bf Survey data}
\end{column}
\begin{column}{0.3\textwidth}
\center {\bf Citizen science data}
\end{column}
\begin{column}{0.3\textwidth}
\center {\bf Declaration data}
\end{column}
\end{columns}

\vspace{\baselineskip}
 
\begin{columns}
\begin{column}{0.1\textwidth}
\center \Huge \textbf{\textcolor{BaptisteBlue}{\ding{58}}}
\normalsize
\end{column}
\begin{column}{0.3\textwidth}
\normalsize
Standardized sampling plan \\
High quality data
\end{column}
\begin{column}{0.3\textwidth}
Access to more data \\
Exact locations available
\end{column}
\begin{column}{0.3\textwidth}
Mandatory declaration \\
Massive data
\end{column}
\end{columns}

\vspace{\baselineskip}

\begin{columns}
\begin{column}{0.1\textwidth}
\center \Huge \fontsize{45}{15}{\textbf{\textcolor{BaptisteBlue}{-}}}
\normalsize
\end{column}
\begin{column}{0.3\textwidth}
\normalsize
Small sample size
\end{column}
\begin{column}{0.3\textwidth}
Opportunistic (or even preferential) sampling
\end{column}
\begin{column}{0.3\textwidth}
Aggregated at the scale of administrative units
\end{column}
\end{columns}

\begin{columns}
\begin{column}{0.1\textwidth}
\center \footnotesize {\bf Examples}
\end{column}
\begin{column}{0.3\textwidth}
\center
\includegraphics[width=2cm]{images/EVHOE_stations.jpg}
\end{column}
\begin{column}{0.3\textwidth}
\center
\includegraphics[width=3cm]{images/bird_apps.jpg}
\end{column}
\begin{column}{0.3\textwidth}
\center
\includegraphics[width=2.5cm]{images/harvest_picture.PNG}
\end{column}
\end{columns}

\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.3\textwidth}
\center \scriptsize
EVHOE data, Bay of Biscay \\ (marine ecology)
\end{column}
\begin{column}{0.3\textwidth}
\center \scriptsize
Ebird application \\ (ornithology)
\end{column}
\begin{column}{0.3\textwidth}
\center \scriptsize
Harvest data, Wisconsin \\ (hunting)
\end{column}
\end{columns}

---
\btVFill
\begin{center} \Large
\textbf{How to integrate all these datasources?}
\vspace{\baselineskip}
\large
(especially when they do not have the same spatial resolution)
\normalsize

\btVFill

\end{center}
\onslide<2>{
\normalsize
\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Some specific application in the context of fishery science: \\
\scriptsize
\textit{Alglave Baptiste, Rivot Etienne, Etienne Marie-Pierre, Woillez Mathieu, Thorson James T, Vermard Youen (2022). \textbf{Combining scientific survey and commercial catch data to map fish distribution.} ICES Journal of Marine Science IN PRESS. \url{https://doi.org/10.1093/icesjms/fsac032}}
\vspace{\baselineskip}
}

# Material and method

### Commercial catch declarations data in fishery science

```{r,echo=F,fig.align='center',out.width="120%"}

if(run_codes){
  
  load("map/ICES_rect.RData")
  load("res/points_sf.RData")

  #-------------------
  ## Logbook data plot
  #-------------------
  logbooks_df <- points_sf %>%
    # filter(str_detect(SI_DATE,"11/2018")) %>%
    group_by(ICESNAME_1) %>%
    dplyr::summarise(Catch = sum(LE_KG_Solea_solea)/1000,
                     Effort = sum(INTV)/60)
  
  logbooks_sf <- st_join(ICES_rect,logbooks_df) %>%
    filter(!is.na(Effort))
  
  Logbooks_data <- ggplot()+
    geom_sf(data = ICES_rect,fill="skyblue",alpha=0.25)+
    geom_sf(data=logbooks_sf,aes(fill=Catch))+
    geom_sf(data = mapBase)+
    scale_fill_distiller(palette = "Spectral")+
    theme(panel.background = element_rect(fill = "skyblue"),
          plot.title = element_text(hjust=0.5),
          legend.position = "none")+
    geom_sf(col="black")+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    annotation_scale(location = "bl", line_width = .5)+
    annotation_north_arrow(location = "tl", height = unit(0.7, "cm"),
                           width = unit(0.7, "cm"))
  
  ggsave(Logbooks_data,filename = "images/logbooks_data.png",width = 5,height = 5)
  
  #---------------
  ## VMS data plot
  #---------------
  ## Aggregate/discretize data
  vms_df <- points_sf %>%
    mutate(long = sf::st_coordinates(.)[,1],
           lati = sf::st_coordinates(.)[,2]) %>%
    as.data.frame %>%
    dplyr::select(-geometry) %>%
    mutate(long = round(long,digits = 2),
           lati = round(lati,digits = 2)) %>%
    group_by(long,lati) %>%
    dplyr::summarise(Effort = sum(INTV)/60)
    
  vms_sf <- st_as_sf(vms_df,coords = c("long","lati"),crs=grid_projection)
  
  ## Build polygon
  # Coordinates Bay of Biscay
  grid_xmin <- -6
  grid_xmax <- 0
  grid_ymin <- 42
  grid_ymax <- 48
  grid_limit <- extent(c(grid_xmin,grid_xmax,grid_ymin,grid_ymax))
  
  # Build grid
  grid <- raster(grid_limit)
  res(grid) <- 0.025
  crs(grid) <- "+proj=longlat +datum=WGS84"
  gridpolygon <- rasterToPolygons(grid)
  gridpolygon$layer <- c(1:length(gridpolygon$layer))
  gridpolygon_sf <- st_as_sf(gridpolygon)
  
  vms_sf_2 <- st_join(gridpolygon_sf,points_sf)
  vms_sf_3 <- vms_sf_2 %>%
    group_by(layer) %>%
    dplyr::summarise(Effort = sum(INTV)/60)
  
  vms_sf_3 <- vms_sf_3 %>%
    filter(!is.na(Effort))
  
  # save(data=vms_sf_3,file="res/vms_sf_3.RData")
  
  vms_data <- ggplot()+
    geom_sf(data = ICES_rect,fill="skyblue",alpha=0.25)+
    geom_sf(data=vms_sf_3,aes(col=Effort,fill=Effort))+
    geom_sf(data = ICES_rect,alpha=0)+
    geom_sf(data = mapBase)+
    scale_color_distiller(direction = 1,palette = "OrRd")+ # palette = "OrRd"
    scale_fill_distiller(direction = 1,palette = "OrRd")+ # ,palette = "Spectral"
    theme(panel.background = element_rect(fill = "skyblue"),
          plot.title = element_text(hjust=0.5),
          legend.position = "none")+
    geom_sf(col="black")+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)
  
  ggsave(filename = "images/vms_data.png",width = 5,height = 5)
  
}

```


\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\center {\bf Logbook landings} \\
\scriptsize (Sole, trawlers OTB-DEF, 2018) 
\end{column}
\begin{column}{0.45\textwidth}
\center {\bf Fishing locations (VMS)} \\
\scriptsize (Trawlers OTB-DEF, 2018)
\end{column}
\end{columns}

\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\includegraphics[width=5cm]{images/logbooks_data.png}
\end{column}
\begin{column}{0.45\textwidth}
\includegraphics[width=5cm]{images/vms_data.png}
\end{column}
\end{columns}

\begin{columns}
\begin{column}{0.1\textwidth}
\center \scriptsize {\bf Spatial \\ resolution}
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize Catch are daily declared at the resolution of ICES rectangles
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize VMS pings are vessels GPS locations emitted each hour
\end{column}
\end{columns}
\tiny
\onslide<2>{
\begin{columns}
\begin{column}{0.1\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\end{column}
\begin{column}{0.45\textwidth}
\center \scriptsize \textbf{\textcolor{BaptisteBlue}{\ding{224}}  Refine landings spatial resolution}
\end{column}
\end{columns}
}

### Two alternative procedures to reallocate catches

\center

\includegraphics[width=11cm]{images/realloc.png}

\onslide<2-3>{

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{4cm} M{4cm} }
  \textcolor{BaptisteRed}{\textbf{Current situation}} & 
  $Y_i | \textcolor{BaptisteBlue}{S}(x_i), x_i \sim \mathcal{L}_Y(\textcolor{BaptisteBlue}{S}(x_i),\xi,\sigma^2)$          &
  $Y_i=\frac{\textcolor{BaptisteLightGreen}{D_j}}{ \operatorname{n}(\textcolor{BaptisteLightGreen}{\mathcal{P}_j})}=\textcolor{BaptisteRed}{Y_i^*}$ \\
  \end{tabular}
\end{table}

}

\onslide<3>{

\begin{table}
  \centering \scriptsize
  \begin{tabular}{ M{2cm} M{2cm} M{4cm} M{2cm} }
  \textcolor{BaptisteLightGreen}{\textbf{Alternative solution}} & 
  $\textcolor{BaptisteLightGreen}{D_j}=\sum_{\textcolor{BaptisteLightGreen}{i \in \mathcal{P}_j}}{Y_{i}}$          &
  $\textcolor{BaptisteLightGreen}{D_j} | \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\textcolor{BaptisteLightGreen}{\mathcal{P}_j} \sim \mathcal{L}_D( \textcolor{BaptisteBlue}{S}_{\textcolor{BaptisteLightGreen}{\mathcal{P}_j}},\xi,\sigma^2)$
  & \textcolor{BaptisteBlue}{\ding{224}}  Match $\mathcal{L}_D$ and $\mathcal{L}_Y$ moments \tiny (appendix) \\ 
  \end{tabular}
\end{table}

}

### Simulation-estimation and case study


```{r,echo=F}

if(run_codes){
  ## Load simulated data
  load("res/simu_df.RData")
  load("res/list_input.RData")
  
  simu_df_2 <- simu_df %>%
    mutate(Ab = sum(S_x))
  
  loc_x <- list_input$loc_x
  sci.data_df <- data.frame(cell = list_input$index_sci_i,
                            y_sci = list_input$y_sci_i) %>%
    inner_join(loc_x[,c("x","y","cell","ICESNAME")])
  
  com.data_df <- data.frame(cell = list_input$index_i,
                            y_com = list_input$y_i2) %>%
    inner_join(loc_x[,c("x","y","cell","ICESNAME")]) %>%
    group_by(x,y,cell,ICESNAME) %>%
    dplyr::summarise(n=n())
  
  ## Grid data
  grid <- raster(grid_limit)
  res(grid) <- 0.05
  crs(grid) <- "+proj=longlat +datum=WGS84"
  gridpolygon <- rasterToPolygons(grid)
  gridpolygon$layer <- c(1:length(gridpolygon$layer))
  gridpolygon_sf <- st_as_sf(gridpolygon)
  
  simu_sf <- st_as_sf(simu_df_2,coords = c("long","lati"),crs=grid_projection)
  
  simu_sf_2 <- st_join(gridpolygon_sf,simu_sf) %>%
    filter(!is.na(S_x))
  
  ## Plot data
  data_plot <- ggplot()+
    geom_sf(data=simu_sf_2,aes(fill=log(S_x)),col=NA,alpha=0.5)+
    geom_sf(data=simu_sf_2[which(simu_sf_2$ICESNAME %in% com.data_df$ICESNAME),],
            aes(fill=log(S_x),col=log(S_x)))+
    scale_fill_distiller(palette = "Spectral")+
    scale_color_distiller(palette = "Spectral")+
    geom_point(data=sci.data_df,aes(x=x,y=y),fill="#619CFF",shape=21,size=1)+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5),
          legend.title = element_blank(),
          legend.position = "none")+
    geom_sf(data=ICES_rect,alpha=0)+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  ggsave(filename = "images/data_plot.png",width = 5,height = 5)
  
}

```


\begin{columns}
\begin{column}{0.5\textwidth}

\center
\textbf{Simulation-estimation}

\end{column}
\begin{column}{0.5\textwidth}

\end{column}
\end{columns}

\tiny \vspace{\baselineskip}

\begin{columns}
\begin{column}{0.5\textwidth}


\begin{columns}
\begin{column}{0.45\textwidth}

\includegraphics[width=3cm]{images/data_plot.png}

\end{column}
\begin{column}{0.55\textwidth}
\footnotesize
\textbf{Simulation}
\tiny
\begin{itemize}
\item \scriptsize \textcolor{BaptisteBlue}{\textbf{Latent field}} \tiny (\textcolor{BaptisteOrange}{covariate} + \textcolor{BaptisteBrown}{spatial random effect})
\item \scriptsize \textbf{Commercial data} \tiny (3000 samples over 2/3 of the area)
\item \scriptsize \textcolor{BaptisteLightGreen}{\textbf{Reallocation process}} \tiny (10 locations per declaration)
\item \scriptsize \textcolor{SurveyBlue}{\textbf{Scientific data}} \tiny (100 samples over the whole the area)
\end{itemize}

\end{column}
\end{columns}

\scriptsize
\vspace{\baselineskip}

\onslide<2-4>{
\footnotesize
\textbf{Estimation} \scriptsize \\
Comparison of 3 model configurations: \\
\tiny \vspace{\baselineskip} \scriptsize
1/ Model fitted to \textbf{\textcolor{SurveyBlue}{scientific data}} only \\
\tiny \vspace{\baselineskip} \scriptsize
2/ \textcolor{BaptisteDarkGrey}{\textbf{Integrated model}} (= \textbf{\textcolor{SurveyBlue}{scientific}} + \textbf{commercial data}) with \textcolor{BaptisteRed}{commercial likelihood built on $\bf{Y_i^*}$} \\
\tiny \vspace{\baselineskip} \scriptsize
3/ \textcolor{BaptisteDarkGrey}{\textbf{Integrated model}} with \textcolor{BaptisteLightGreen}{commercial likelihood built on $\bf{D_j}$} \\
\tiny \vspace{\baselineskip}

Estimation realized through TMB (Template Model Builder) \\
100 runs of simulation-estimation

}

\end{column}
\begin{column}{0.5\textwidth}

\onslide<3-4>{

\footnotesize
\textbf{Model evaluation} \scriptsize \\
1/ Mean square prediction error \\
$$MSPE=\frac{\sum_{x=1}^n (\textcolor{BaptisteBlue}{S(x)} - \textcolor{BaptisteBlue}{\hat{S}(x)} ) ^2}{n}$$

\vspace{\baselineskip}

2/ Covariate effect (or species-habitat relationship): \\
$$\textcolor{BaptisteOrange}{\beta_S} = 2 \, \, \, \text{versus} \, \, \, \textcolor{BaptisteOrange}{\hat{\beta}_S}$$
\vspace{\baselineskip}

}

\onslide<4>{

\normalsize
\begin{center}
\textbf{Case study:} \scriptsize Sole in the Bay of Biscay \\
\end{center}

\begin{columns}
\begin{column}{0.5\textwidth}
\center
\includegraphics[width=2cm]{images/solea_solea.png}
\vspace{\baselineskip}
\vspace{\baselineskip}
\end{column}
\begin{column}{0.5\textwidth}
\tiny \textcolor{SurveyBlue}{\textbf{Survey data:}} Orhago\\
\textbf{Commercial data:} OTB-DEF trawlers (to ease convergence onboard observer data were integrated in the fit)\\
\textbf{Fitted models:} same as simulations\\
\textcolor{BaptisteOrange}{\textbf{Covariate:}} substrate

\normalsize \vspace{\baselineskip}
 
\end{column}
\end{columns}

}

\end{column}
\end{columns}


# Results

### Simulation-estimation

```{r,echo=F}

if(run_codes){
  
  ######################
  ## Parameter estimates
  ######################
  load("res/Results_full_multi_square.RData")
  
  Results_plot <- Results_2 %>%
    filter(converge == 0) %>%
    filter(simu_type == "Unsampled Rectangles")
  
  Results_plot[,"RelBias_N"]=(Results_plot[,"N_est"]-Results_plot[,"N_true"])/Results_plot[,"N_true"]
  Results_plot[,"RelBias_N.2"]=(Results_plot[,"N_est.2"]-Results_plot[,"N_true.2"])/Results_plot[,"N_true.2"]
  Results_plot[,"RelBias_beta"]=(Results_plot[,"beta1_est"]-Results_plot[,"beta1_true"])/Results_plot[,"beta1_true"]
  
  Results_plot$obs <- NA
  Results_plot$obs[which(Results_plot$aggreg_obs == T)] <- "Dj"
  Results_plot$obs[which(Results_plot$aggreg_obs == F)] <- "Yi*"
  Results_plot$obs[which(Results_plot$Estimation_model == 2)] <- "Scientific model"
  Results_plot$obs <- factor(Results_plot$obs,levels = c("Yi*","Dj","Scientific model"))
  
  Results_plot$Model[which(Results_plot$Model == "Scientific model")] <- "Scientific"
  Results_plot$Model[which(Results_plot$Model == "Commercial model")] <- "Commercial"
  Results_plot$Model[which(Results_plot$Model == "Integrated model")] <- "Integrated"
  
  Results_plot <- Results_plot %>%
    filter(Model != "Commercial")
  
  # Results_plot_fullArea <- Results_plot
  # Results_plot_UnsampArea <- Results_plot
  
  beta_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = beta1_est,
                     fill = obs))+
    geom_hline(yintercept = 0,linetype="dashed")+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab(TeX("$\\beta_S$")) +
    xlab("")+
    geom_hline(yintercept = 2,col="red",linetype="dashed")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))
  
  MSPE_S_plot <- ggplot()+
    geom_boxplot(data = Results_plot,
                 aes(x = Model,
                     y = mspe,
                     fill = obs))+
    theme_bw()+
    theme(legend.title = element_blank(),
          legend.position = "none",
          aspect.ratio = 1)+
    # facet_wrap(.~simu_type)+
    ylab("MSPE")+xlab("")+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    ylim(0,NA)
  
  legend <- as_ggplot(cowplot::get_legend(MSPE_S_plot+theme(legend.position="bottom",legend.title = element_blank())))
  
  pl_plot <- plot_grid(MSPE_S_plot,
                       beta_plot,
                       ncol = 1,
                       legend,
                       align="hv",
                       rel_heights = c(1,1,0.15))
  
  ggsave(filename = "images/res_simu_plot.png",width = 4,height = 7.5)
  
  #######
  ## Maps
  #######
  simu_plot <- ggplot(simu_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Simulated latent field")+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  load("res/fit_IM_res_sci.RData")
  sci_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  sci_plot <- ggplot(sci_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Scientific model")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#619CFF",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  load("res/fit_IM_res_int_Yi.RData")
  int_Yi_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  int_Yi_plot <- ggplot(int_Yi_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Commercial likelihood on Yi*")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  load("res/fit_IM_res_int_Dj.RData")
  int_Dj_df <- data.frame(loc_x,S_x=fit_IM_res$Report$S_x)
  int_Dj_plot <- ggplot(int_Dj_df)+
    geom_point(aes(x=x,y=y,col=S_x/sum(S_x)),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral")+
    ggtitle("Commercial likelihood on Dj")+
    theme_bw()+
    theme(plot.title = element_text(colour = "#00BA38",hjust = 0.5,face = "bold"),
          plot.subtitle = element_text(hjust = 0.5),
          legend.position = "none")+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  map_simu <- plot_grid(simu_plot,sci_plot,int_Yi_plot,int_Dj_plot)

  ggsave(filename = "images/map_simu_plot.png",width = 6,height = 7.5)
  
}

```

\center

\begin{columns}
\begin{column}{0.4\textwidth}

\center
\includegraphics[width=4cm]{images/res_simu_plot.png}

\end{column}

\begin{column}{0.6\textwidth}
\center

\includegraphics[width=5.5cm]{images/map_simu_plot.png}
\vspace{\baselineskip}

\end{column}

\end{columns}


### Case study: Sole in the Bay of Biscay

```{r,echo=F}

if(run_codes){

  ## Load data
  load("res/sci_df.RData")
  
  load("res/realloc_rest_df.RData")
  
  load("res/no.realloc_df.RData")
  
  load("res/est_par_df_full_3.RData")
  
  ## Plot maps
  no.realloc_plot <- ggplot(no.realloc_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Commercial likelihood on Yi*")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#F8766D",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  realloc_rest_plot <- ggplot(realloc_rest_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Commercial likelihood on Dj")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#00BA38",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  sci_plot <- ggplot(sci_df)+
    geom_point(aes(x=x,y=y,col=S_x),shape=15,size=2)+
    scale_color_distiller(palette = "Spectral",limits=c(0,NA))+
    ggtitle("Scientific model")+
    theme_bw()+
    theme(legend.position = "none",
          plot.title = element_text(colour = "#619CFF",hjust = 0.5,face = "bold"))+
    geom_sf(data = mapBase)+
    coord_sf(xlim = c(-6,0), ylim = c(43,48), expand = FALSE)+
    xlab("")+ylab("")
  
  # plot(log(no.realloc_df$S_x),log(sci_df$S_x))
  # cor(log(no.realloc_df$S_x),log(sci_df$S_x),method = "spearman")
  # plot(log(realloc_rest_df$S_x),log(sci_df$S_x))
  # cor(log(realloc_rest_df$S_x),log(sci_df$S_x),method = "spearman")
  
  case_study_plot <- plot_grid(NULL,sci_plot,no.realloc_plot,realloc_rest_plot,align="hv")
  
  ggsave("images/case_study_plot.png",width = 6, height = 7.5)
  
  ## Parameter estimates
  est_par_df_full_3$lkl[which(est_par_df_full_3$lkl == "Yi")] <- "Yi*"
  est_par_df_full_3$lkl <- factor(est_par_df_full_3$lkl,levels = c("Dj","Yi*","Scientific model"))
  est_par_df_full_3 <- est_par_df_full_3 %>%
    filter(par_names != "substr_Sand_Coarse_substrate")
  par_plot <- ggplot(est_par_df_full_3, aes(y=par_val, x=par_names))+
    geom_point(
      aes(color = lkl),
      position = position_dodge(0.5),
      size=2
    )+
    geom_errorbar(aes(ymin = CI.inf, ymax = CI.sup, color = lkl),
                  position = position_dodge(0.5),width=0.4
    )+
    scale_color_manual(breaks = c("Scientific model",
                                  "Yi*",
                                  "Dj"),
                       values=c("#619CFF","#F8766D","#00BA38"))+
    geom_hline(yintercept=0, linetype="dashed", color = "red",alpha=0.4)+
    xlab("")+ylab("")+
    theme_bw()+
    ggtitle("Parameters estimates")+
    theme(plot.title = element_text(hjust = 0.5,face = "bold"),
          legend.title = element_blank(),
          legend.position = "bottom",
          aspect.ratio = 1)+
    coord_flip()+
    scale_x_discrete(labels=c('k_com'=parse(text = TeX('$k_{com}$')),
                              'Sigma_com'=parse(text = TeX('$\\sigma_{com}$')),
                              'q1_com'=parse(text = TeX('$\\xi_{com}$')),
                              'Sigma_sci'=parse(text = TeX('$\\sigma_{sci}$')),
                              'q1_sci'=parse(text = TeX('$\\xi_{sci}$')),
                              'Range'="Range",
                              'MargSD'="M. var.",
                              'substr_Mud_sediment'=parse(text = TeX('$\\beta_{S}$')),
                              'intercept'=parse(text = TeX('$\\mu$'))))

  ggsave("images/par_plot.png",width = 6/1.75,height = 7.5/1.75)
  
}

```

\center

\begin{columns}
\begin{column}{0.4\textwidth}

\begin{center}
\includegraphics[width=4.5cm]{images/par_plot.png}
\end{center}
\scriptsize
\onslide<2>{

The \textcolor{BaptisteDarkGrey}{\textbf{integrated model}} fitted to \textcolor{BaptisteLightGreen}{$\bf{D_j}$}:

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Recovers the species-habitat relationship ($\bf{\textcolor{BaptisteOrange}{\beta_S}}$)

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Modifies the \textbf{contrasts of the map} \tiny (shape and intensity of the hotspots/coldspots) \scriptsize

}

\end{column}

\begin{column}{0.6\textwidth}
\center
\includegraphics[width=5.5cm]{images/case_study_plot.png}
\vspace{\baselineskip}

\end{column}

\end{columns}


# Discussion

### Discussion

\begin{itemize}

\item \textcolor{BaptisteDarkGrey}{\textbf{Integrated framework}} that combines \textcolor{BaptisteLightGreen}{\textbf{catch declarations data}} (rough resolution) and \textcolor{SurveyBlue}{\textbf{scientific data}} (exact locations) \\
\textcolor{BaptisteBlue}{\ding{224}} Allows to estimate the \textcolor{BaptisteOrange}{\textbf{habitat effect}} through commercial data \\
\textcolor{BaptisteBlue}{\ding{224}} Modifies the \textbf{contrasts of the map} (hotspots vs. coldspots)

\tiny \vspace{\baselineskip} \normalsize

\onslide<2-4>{

\item \textbf{Some limits:}

\textcolor{BaptisteBlue}{\ding{224}} How to ease convergence ? \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Need to make the hypothesis that fishing locations ($\textcolor{BaptisteLightGreen}{\mathcal{P}_j}$) are known

}

\tiny \vspace{\baselineskip} \normalsize

\onslide<3-4>{

\item \textbf{Is it a generic framework ?} \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} The overall approach is, \scriptsize \\ \textit{(i.e. modelling observed aggregated observations as a sum of latent punctual observations)}

\normalsize \textbf{\textcolor{BaptisteBlue}{\ding{224}}} But need to adapt the observation model to the data \scriptsize \\ \textit{(here zeroinflated positive continuous data)}

}

\tiny \vspace{\baselineskip} \normalsize
 
\onslide<4>{

\item \textbf{ Change of support applications} \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Increasing amount of available data that may face such issues \\

\textbf{\textcolor{BaptisteBlue}{\ding{224}}} Here is one proposition to integrate aggregated data in SDM \\

}


\end{itemize}

#

\tiny \vspace{\baselineskip}

\centering \Large \textcolor{BaptisteGrey}{\textbf{Thank you for your attention!}}

\tiny \vspace{\baselineskip}

\begin{figure}
    \includegraphics[width=11cm]{images/front_page.png}
\end{figure}

#

\footnotesize

\textbf{Punctual observation model} ($Y_i$):

\scriptsize $\operatorname{L}(y,\mu,\sigma^2)$ is the lognormal likelihood for observation $y$, mean $\mu$ and variance $\sigma^2$

$Y$ and $D$ are supposed conditional on S and x \footnotesize

$$
\operatorname{P}\left(Y_i=y_{i} \right) =
\left\{
    \begin{array}{ll}
        p_i & \text { if } y_{i}=0 \\
        \left(1-p_i\right) \cdot \operatorname{L}\left(y_{i },\mu_i=\frac{S(x_i)}{\left(1 - p_i\right)},\sigma^{2} \right) & \text { if } y_{i} > 0
    \end{array}
\right.
$$

$$p_{i}=\exp(-e^\xi .S(x_{i}))$$

\tiny \vspace{\baselineskip} \footnotesize

\textbf{Declaration model} ($D_j=\sum_{i \in \mathcal{P}_j}{Y_{i}}$):


\begin{align*}
P(D_j = 0) & = \prod_{i\in \mathcal{P}_j} P(Y_{i} = 0)
                      = \exp{ \left \lbrace- \sum_{i\in \mathcal{P}_j} e^{\xi}. S(x_{i})\right \rbrace} = \pi_j.
\end{align*}

$$\operatorname{P}\left(D_j=d_{j} \vert d_j > 0 \right) =  \operatorname{L}\left(d_{j},\mu_j = E(D_j|d_j>0),\sigma_j^2 = ln(\frac{Var(D_j|d_j>0)}{E(D_j|d_j>0)^2} + 1) \right)$$

$$E(D_j \vert d_j > 0)=\frac{\sum_{i \in \mathcal{P}_j} S(x_{i})}{1-\pi_j}$$

$$Var(D_j \vert d_j > 0) = \frac{\sum_{i \in \mathcal{P}_j} Var(Y_{i})}{1-\pi_j} - \frac{\pi_j}{(1-\pi_j)^2}E(D_j)^2$$

$$Var(Y_{i})=\frac{S(x_{i})^2}{1-p_{i}}(e^{\sigma^2}-(1-p_{i}))$$

