--- 
title: "Accounting for commercial data without reallocationg the catches."
author: "MP Etienne"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Working at the statistical unit scale."
---


```{r include=FALSE}
library(tidyr)
library(ggplot2)
library(purrr)
```


# Model presentation

## Log Normal parametrization 

Many different parametrizations of the log normal exist, We have to choose the most convenient for our purpose

### Version 1

\begin{equation} 
  D \sim \mathcal{LN} (\rho, \sigma^2) \Longleftrightarrow D =e^{\rho + \sigma N}, \ N\sim \mathcal{N}(0,1) .
  (\#eq:LNv1)
\end{equation} 

In this parametrization 
$$E(D) = e^{\rho +\frac{\sigma^2}{2}},\quad Var(D) = \left(e^{\sigma^2}-1\right) e^{2\rho + \sigma^2}$$

### Version 2

\begin{equation} 
  D \sim \mathcal{LN} (\nu, \sigma^2) \Longleftrightarrow D =\mu e^{\sigma N}, \ N\sim \mathcal{N}(0,1) .
  (\#eq:LNv2)
\end{equation} 

In this parametrization 
$$E(D) = \nu e^{\frac{\sigma^2}{2}},\quad Var(D) = \nu^2 \left(e^{\sigma^2}-1\right) e^{ \sigma^2}$$

### Version 3, the mean of the log normal is the actual parameter



\begin{equation} 
  D \sim \mathcal{LN} (\mu, \sigma^2) \Longleftrightarrow D =\mu e^{\sigma N- \frac{\sigma^2}{2}}, \ N\sim \mathcal{N}(0,1) .
  (\#eq:LNv3)
\end{equation} 

In this parametrization 
$$E(D) = \mu ,\quad Var(D) = \mu^2 \left(e^{\sigma^2}-1\right). $$
With this parametrization, 

$$D \sim\mathcal{LN}\left ( E(D), \ln\left\lbrace Var(D)/E(D)^2 +1\right\rbrace\right ).$$
We will use this last parametrization throughout the paper. 

## Model

The model proposed by Baptiste has a hierarchical structure with three main components 


- the biomass latent field $S$, representing the spatial repartition of biomass:

\begin{equation} 
  S(x)  = \exp{ \left \lbrace \alpha_S + \Gamma_S(x)^\intercal \beta_S +\delta(x)\right \rbrace}
  (\#eq:latent)
\end{equation} 


- the preferential sampling density, defined conditionnally to $S$:

\begin{equation} 
  \lambda(x)  = \exp{ \left \lbrace \alpha_X + b \log{\left \lbrace S(x)\right\rbrace} + \Gamma_X(x)^\intercal \beta_X +\eta(x)\right \rbrace}
  (\#eq:pref)
\end{equation} 

- and finally, the observations are defined at the VMS ping scale. $Y_i$ stands for the CPUE at location $x_i$ and is defined conditionnaly on  the Poisson process and the biomass latent field $S$:

\begin{align*} 
  Y_i  &= C_i Z_i,    (\#eq:obs)\\ 
  C_i &\sim \mathcal{B}(1-p_i), \mbox{ with } p_i = \exp{ \left \lbrace  - e^{\xi \mu(x_i) }\right \rbrace}, \nonumber  \\
  Z_i &\sim \mathcal{LN}( \frac{\mu(x_i)}{1-p_i}, \sigma^2),\nonumber \\
  \mu(x_i) &= q S(x_i).\nonumber \\
\end{align*} 


## Potential limitation

The information regarding the catch is not known at the fishing point level (VMS ping) but at the statistical unit, as recorded in the logbook.
The available information on the commercial catch is the declaration $D_j$  at the statistical unit level and the VMS ping location $(x_{j1}, \ldots x_{jn_j})$. $D_j$ is the sum of all individuals catch at the $n_j$ visited fishing points:

\begin{equation*}
  D_{j} = \sum_{i \in  \mathcal{P}_j} Y_i,
\end{equation*} 

$\mathcal{P}_j$ being the vector of all fishing events associated with the logbook entry $j$. 

This diffculty is currently addressed by reallocating the total catch to individual fishing events with a simple proportionality rule:
$$\tilde{Y_i} = \frac{1}{|\mathcal{P}_j|} D_j.$$

This is not completely satisfactory as it might introduce some bias is the total biomass estimation as well as its spatial repetition. 


## Is is a real limitation ?

A strategy to answer this question would be 

1. Simulation study to understand when this reallocation is problematic
2. A new observation model at the statitical unit level
3. Does this new model improves the estimation ?


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
